---
title: "Use of the existing Eagle project vocabularies in the I.Sicily dataset"
author:
- Petra Hermankova^[Johannes Gutenberg University in Mainz, petra.hermankova@uni-mainz.de, https://orcid.org/0000-0002-6349-0540]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: united
    toc: yes
    toc_float: true
    number_sections: true
    toc_depth: 2
    df_print: paged
---

**The aim of this script is to analyse the usage of EAGLE vocabularies in the I.Sicily as part of the FAIR Epigraphy project and the Epigraphy.info working group tasked with cleaning up the EAGLE vocabularies.**

## Environment setup

```{r setup, echo=TRUE, message=FALSE}
library(tidyverse)
library(jsonlite)
library(zen4R)
library(xml2)
library(XML)
```

# Data loading and preparation

##  Load the latest I.Sicily dataset directly from Zenodo

```{r}
download_zenodo("10.5281/zenodo.4431640", path = "./data")
```

## Extract the Zenodo repository
```{r}
unzip("./data/ISicily-v0.3beta.zip", exdir = "./data")
```

## Read and parse the XML files and extract the vocabularies data into a CSV, using python script

We are looking specifically for vocabularies `terms` that contain information about the type of an inscription
`<textClass>`
  `<keywords scheme="http://www.eagle-network.eu/voc/typeins.html">`
    `<term key="funerary" ref="http://www.eagle-network.eu/voc/typeins/lod/92.html">funerary</term>`
  `</keywords>`
`</textClass>`

```{r}
# Enabling reticulate library to run the python scripts within R
library(reticulate)
```

```{python}
# Read and parse the XML files and extract the vocabularies data into a CSV, using python script

#!/usr/bin/env python3
# Epidoc to csv converter
# written by Brian Ballsun-Stanton
# under a MIT License

import glob
import csv
import epidoc
import shutil
import os
import tqdm

PROJECT = "ISicily"
SOURCE_DIR = "./data/ISicily-ISicily-cf52385/inscriptions/"
TARGET_DIR = "xml_to_csv"

# clean target dir by deleting and recreating
shutil.rmtree(TARGET_DIR, ignore_errors=True)
os.mkdir(TARGET_DIR)

docs = []

# get all files in source dir
for file in tqdm.tqdm(glob.glob(f"{SOURCE_DIR}/*.xml")):
    with open(file) as f:
        doc = epidoc.load(f)
    docs.append(doc)
    # break

output_docs = []


# Get Title, All instances of idno and terms
# Terms hide under textClass

for doc in tqdm.tqdm(docs):
    line = {}
    line["title"] = doc.title
    line["idno"] = doc.idno
    line["terms"] = doc.terms
    output_docs.append(line)

# Write to CSV
with open(f"{TARGET_DIR}/{PROJECT}_xml_to_csv_output.csv", "w") as f:
    writer = csv.DictWriter(f, fieldnames=["title", "idno", "terms"])
    writer.writeheader()
    for doc in output_docs:
        writer.writerow(doc)
        
print(doc)
        
```

```{python}
output_docs
```

```{r}
py$output_docs -> output_docs_r
```

```{r}
library(nplyr)
output_docs_r

test<- lapply(output_docs_r, unlist)

head(test)

test[[1]]

output_docs_r %>% 
  map_dfc(identity)

```

NESTED LISTS https://www.tenderisthebyte.com/blog/2019/11/02/notes-from-the-messyverse-tidying-nested-lists/


```{python}
# List all unique keys 

import csv
import pandas as pd
import numpy as np
import json

import csv
keys = set() # create an empty set to store the keys
with open("./xml_to_csv/ISicily_xml_to_csv_output.csv") as f: # open the CSV file
    reader = csv.DictReader(f) # create a reader object
    for row in reader: # loop through each row
        terms = eval(row["terms"]) # convert the terms column to a list of dictionaries
        for term in terms: # loop through each term dictionary
            keys.add(term["key"]) # add the key value to the set
print(keys) # print the set of keys

refs = set() # create an empty set to store the refs
with open("./xml_to_csv/ISicily_xml_to_csv_output.csv") as f: # open the CSV file
    reader = csv.DictReader(f) # create a reader object
    for row in reader: # loop through each row
        terms = eval(row["terms"]) # convert the terms column to a list of dictionaries
        for term in terms: # loop through each term dictionary
            refs.add(term["ref"]) # add the ref value to the set
print(refs) # print the set of keys
```

```{python}
#list of all unique keys with their frequency
import csv
counts = {} # create an empty dictionary to store the counts
with open("./xml_to_csv/ISicily_xml_to_csv_output.csv") as f: # open the CSV file
    reader = csv.DictReader(f) # create a reader object
    for row in reader: # loop through each row
        terms = eval(row["terms"]) # convert the terms column to a list of dictionaries
        for term in terms: # loop through each term dictionary
            key = term["key"] # get the key value
            counts[key] = counts.get(key, 0) + 1 # increment the count for the key or set it to 1 if not in the dictionary
print(counts) # print the dictionary of counts

counts2 = {} # create an empty dictionary to store the counts
with open("./xml_to_csv/ISicily_xml_to_csv_output.csv") as f: # open the CSV file
    reader = csv.DictReader(f) # create a reader object
    for row in reader: # loop through each row
        terms = eval(row["terms"]) # convert the terms column to a list of dictionaries
        for term in terms: # loop through each term dictionary
            ref = term["ref"] # get the ref value
            counts2[ref] = counts.get(ref, 0) + 1 # increment the count for the key or set it to 1 if not in the dictionary
print(counts2) # print the dictionary of counts

```



```{python}
import pandas as pd
df = pd.read_csv("./xml_to_csv/ISicily_xml_to_csv_output.csv") # read the CSV file into a dataframe
df["idno"] = df["idno"].apply(eval) # convert the idno column to a dictionary
df = df.explode("terms") # expand the list of dictionaries into separate rows
df[["idno_filename", "idno_doi"]] = df["idno"][["filename", "doi"]] # extract the filename and doi values from the idno dictionary into separate columns
df[["key", "ref", "text"]] = pd.json_normalize(df["terms"]) # extract the key, ref, and text values from the terms dictionary into separate columns
#df = df.drop(["idno", "terms"], axis=1) # drop the idno and terms columns
df = df.fillna("NA") # fill any empty values with NA
print(df) # print the dataframe

```



```{r}
df <- read.csv("./xml_to_csv/ISicily_xml_to_csv_output.csv")

library(tidyr)
df$idno <- lapply(df$idno, eval) # convert idno column to a list
df$terms <- lapply(df$terms, eval) # convert terms column to a list
df <- unnest(df, c(idno, terms), names_sep="_") # expand the lists into separate rows

library(dplyr)
df <- df %>%
  select(title, #filename = idno["filename"], idno_doi = idno["doi"], 
         key, ref, text) %>% # select and rename columns
  replace_na(list(key = "NA", ref = "NA", text = "NA")) # fill empty values with NA

```












# Explore the `ISicily` vocabularies

```{r}
# load the data from CSV (stored in the JSON structure because of the multivalued attributes)

ISicily <- read_csv("./xml_to_csv/ISicily_xml_to_csv_output.csv", progress = TRUE)
ISicily
```

```{r}
ISicily %>% 
  as_tibble() %>% 
  mutate(
    terms = gsub("'", "\"", terms),
    terms = list(jsonlite::fromJSON(terms))  
    ) %>%
  unnest()
```







# EAGLE vocabularies

```{r}
EAGLE_vocabs<- read.csv("data/queryResults.csv", sep = ",")
head(EAGLE_vocabs)
```

```{r}
EAGLE_typeins<- read.csv("data/EAGLE_typeins_all.csv", sep = ",")
head(EAGLE_typeins)
```

# Use of EAGLE vocabularies in the EDH

The Epigraphic Database Heidelberg (<https://edh-www.adw.uni-heidelberg.de/>) uses the existing vocabularies from EAGLE Project (<https://www.eagle-network.eu/resources/vocabularies/>) in the following five Epidoc XML tags: `Object Type`, `Keywords`, `Material`, `RS Execution`, `RS Decoration`.

Example of record in XML:

```         
<support>
  <objectType ref="http://www.eagle-network.eu/voc/objtyp/lod/257">Tafel</objectType>
</support>
```

In our processed version of the EDH dataset, all records consist of the following attributes:

-   Eagle Linked Open Data numeric code for vocabulary, i.e. 257, extracted from the reference within the Epidoc XML tag.

-   Free text description, extracted from the XML tag.

See the raw data below:

```{r, select attributes}
EDH_eagle<- EDH %>% 
  select(layout_execution, layout_execution_text, support_objecttype, support_objecttype_text, support_material, support_material_text, support_decoration, keywords_term, keywords_term_text, type_of_inscription_clean)

EDH_eagle
```

## Inscriptions with missing data from XML files

In 2021, the total of 346 record were missing information extracted from XML files (due to delay in availability of published data through EDH data dumps on their website). However, at least partial information about them could be extracted from the then existing EDH API. For the purpose of the current evaluation of the Eagle vocabularies are these 346 records considered as missing as we cannot access their respective XML files with vocabularies.

```{r}
EDH %>% 
  filter(is.na(support_objecttype)) -> missingXML
missingXML
```

```{r, echo=FALSE, eval=FALSE}
EDH_missingXML_json <- jsonlite::toJSON(missingXML)

write(EDH_missingXML_json, file="data/EDH_missingXML_2021.json")
```

## The total number of Eagle vocabularies in EDH dataset

```{r}
#object
EDH_eagle %>% 
  filter(!is.na(support_objecttype) & support_objecttype != "") %>% nrow() -> object_total

#type inscription
EDH_eagle %>% 
  filter(!is.na(keywords_term) & keywords_term != "" ) %>% nrow() -> typeinsc_total

#material
EDH_eagle %>% 
  filter(!is.na(support_material) & support_material != "") %>% nrow() -> material_total

#writing
EDH_eagle %>% 
  filter(!is.na(layout_execution) & layout_execution != "") %>% nrow() -> writing_total

#decoration
EDH_eagle %>% 
  filter(!is.na(support_decoration) & support_decoration != "") %>% nrow() -> decor_total


#how many Eagle vocabularies has been used in the EDH
Eagle_total <- object_total + typeinsc_total + material_total + writing_total + decor_total
Eagle_total
```

## Inscription type

Attributes categorising the type of inscription, used `r typeinsc_total` times.

XML: Keywords tag, term tag.

Example of record in XML:

```         
<keywords>
  <term ref="http://www.eagle-network.eu/voc/typeins/lod/92">Grabinschrift</term>
</keywords>
```

### Display the first six values for illustration

```{r}
EDH_eagle %>% 
  select(keywords_term, keywords_term_text, type_of_inscription_clean) %>%
  head()
```

### List of all related Eagle vocabularies and their count

```{r}
EDH_eagle %>% 
  select(keywords_term, keywords_term_text) %>% 
  count(keywords_term, keywords_term_text, sort=TRUE) -> insc_type_overview_xml

EDH_eagle %>% 
  select(keywords_term, keywords_term_text,type_of_inscription_clean) %>% 
  count(keywords_term, keywords_term_text, type_of_inscription_clean, sort=TRUE) -> insc_type_overview_all
```

```{r}
write_csv(insc_type_overview_xml, "./EDH_inscription_type_eagle_vocab_xml.csv", col_names = TRUE)
```

```{r}
insc_type_overview_xml
```


### Merge with EAGLE LOD data


```{r}
EDH_eagle
```

```{r}
EDH_eagle$keywords_term <- as.numeric(EDH_eagle$keywords_term)


EAGLE_typeins_all<- EDH_eagle %>% dplyr::left_join(EAGLE_typeins, by=c("keywords_term"="EAGLE_lod_id"), multiple="first")

EAGLE_typeins_all %>% 
  select(concept, prefLabel, keywords_term_text, type_of_inscription_clean) %>% 
  count(concept, prefLabel, keywords_term_text, sort=TRUE) -> EDH_EAGLE_usage

EDH_EAGLE_usage
```
#### Save as CSV
```{r}
write_csv(EDH_EAGLE_usage, file = "./data/EDH_EAGLE_usage_typeinsc.csv", col_names = TRUE)
```



### Total number of unique vocabularies

```{r}
length(unique(EDH_eagle$keywords_term))
```

### Overview of the ten most common vocabularies

#### Keyword term 92 (Sepulcralis)

<https://www.eagle-network.eu/voc/typeins/lod/92.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 92) %>% 
  count(keywords_term_text, sort=TRUE)
```

#### Keyword term 143 (Ignoratur)

<https://www.eagle-network.eu/voc/typeins/lod/143.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 143) %>% 
  count(keywords_term_text, sort=TRUE)
```

#### Keyword term 80 (Weihinschrift)

<https://www.eagle-network.eu/voc/typeins/lod/80.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 80) %>% 
  count(keywords_term_text, sort=TRUE)
```

#### Keyword term 311 (Besitzer-/Herstellerinschrift)

<https://www.eagle-network.eu/voc/typeins/lod/311.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 311) %>% 
  count(keywords_term_text, sort=TRUE)
```

#### Keyword term 69 (Honorific inscription)

<https://www.eagle-network.eu/voc/typeins/lod/69.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 69) %>% 
  count(keywords_term_text, sort=TRUE)
```

#### Keyword term 261 (Bau-/Stifterinschrift)

<https://www.eagle-network.eu/voc/typeins/lod/261.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 261) %>% 
  count(keywords_term_text, sort=TRUE)
```

#### Keyword term 102 (Meilen-/Leugenstein)

<https://www.eagle-network.eu/voc/typeins/lod/102.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 102) %>% 
  count(keywords_term_text, sort=TRUE)
```

#### Keyword term 115 (Aufschrift)

<https://www.eagle-network.eu/voc/typeins/lod/115.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 115) %>% 
  count(keywords_term_text, sort=TRUE)
```

#### Keyword term 73 (Akklamation)

<https://www.eagle-network.eu/voc/typeins/lod/73.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 73) %>% 
  count(keywords_term_text, sort=TRUE)
```

#### Keyword term 91 (Militärdiplom)

<https://www.eagle-network.eu/voc/typeins/lod/91.html>

```{r}
EDH_eagle %>% 
  filter(keywords_term == 91) %>% 
  count(keywords_term_text, sort=TRUE)
```

### Missing Eagle LOD, text present

```{r}
EDH_eagle %>% 
  select(keywords_term, keywords_term_text) %>% 
  filter(keywords_term == "") %>% 
  count(keywords_term_text, sort=TRUE)
```

### All unique values of text input

```{r}
unique(EDH_eagle$keywords_term_text)
```

## Object

Attributes categorising the inscribed object, used `r object_total` times.

XML: Support tag, tag objectType.

Example of record in XML:

```         
<support>
  <objectType ref="http://www.eagle-network.eu/voc/objtyp/lod/257">Tafel</objectType>
</support>
```

### Display the first six values for illustration

```{r, head objecttype}
EDH_eagle %>% 
  select(support_objecttype, support_objecttype_text) %>% 
  head()
```

### List of all related Eagle object vocabularies and their count

```{r}
EDH_eagle %>% 
  select(support_objecttype, support_objecttype_text) %>% 
  count(support_objecttype, sort=TRUE)
```

### Total number of unique object vocabularies

```{r}
length(unique(EDH_eagle$support_objecttype))
```

### Overview of the ten most common vocabularies

#### Object type 2 (ignoratur)

<http://www.eagle-network.eu/voc/objtyp/lod/2.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 2) %>% 
  count(support_objecttype_text, sort=TRUE)
```

#### Object type 257 (Tafel)

<http://www.eagle-network.eu/voc/objtyp/lod/257.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 257) %>% 
  count(support_objecttype_text, sort=TRUE)
```

#### Object type 29 (Altar)

<http://www.eagle-network.eu/voc/objtyp/lod/29.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 29) %>% 
  count(support_objecttype_text, sort=TRUE)
```

#### Object type 250 (Stele)

<http://www.eagle-network.eu/voc/objtyp/lod/250.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 250) %>% 
  count(support_objecttype_text, sort=TRUE)
```

#### Object type 140 (Instrumentum domesticum)

<http://www.eagle-network.eu/voc/objtyp/lod/140.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 140) %>% 
  count(support_objecttype_text, sort=TRUE)
```

#### Object type 57 (Statue base)

<http://www.eagle-network.eu/voc/objtyp/lod/57.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 57) %>% 
  count(support_objecttype_text, sort=TRUE)
```

#### Object type 189 (Block)

<http://www.eagle-network.eu/voc/objtyp/lod/189.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 189) %>% 
  count(support_objecttype_text, sort=TRUE)
```

#### Object type 35 (Architekturteil)

<http://www.eagle-network.eu/voc/objtyp/lod/35.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 35) %>% 
  count(support_objecttype_text, sort=TRUE)
```

#### Object type 214 (Sarkophag)

<http://www.eagle-network.eu/voc/objtyp/lod/214.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 214) %>% 
  count(support_objecttype_text, sort=TRUE)
```

#### Object type 89 (Meilen-/Leugenstein)

<http://www.eagle-network.eu/voc/objtyp/lod/89.html>

```{r}
EDH_eagle %>% 
  filter(support_objecttype == 89) %>% 
  count(support_objecttype_text, sort=TRUE)
```

### Missing Eagle vocabulary, but text present

```{r}
EDH_eagle %>% 
  select(support_objecttype, support_objecttype_text) %>% 
  filter(support_objecttype == "") %>% 
  count(support_objecttype_text, sort=TRUE)
```

### List of all vocabularies, their text description and count

```{r}
EDH_eagle %>% 
  select(support_objecttype, support_objecttype_text) %>% 
  count(support_objecttype, support_objecttype_text, sort=T)
```

### List of all unique values of text input

```{r}
unique(EDH_eagle$support_objecttype_text)
```


## Material

Attributes categorising the inscribed material, used `r material_total` times.

XML: Support tag, material tag.

Example of record in XML (with missing Eagle LOD):

```         
<support>
  <material>Marmor, geädert / farbig</material>
</support>
```

### Display the first six values for illustration

```{r}
EDH_eagle %>% 
  select(support_material, support_material_text) %>%
  head()
```

### List of all related Eagle vocabularies and their count

```{r}
EDH_eagle %>% 
  select(support_material, support_material_text) %>% 
  count(support_material, sort=TRUE)
```

### Total number of unique vocabularies

```{r}
length(unique(EDH_eagle$support_material))
```

### Overview of the ten most common vocabularies

#### Material 138 (ignoratur)

<https://www.eagle-network.eu/voc/material/lod/138.html>

```{r}
EDH_eagle %>% 
  filter(support_material == 138) %>% 
  count(support_material_text, sort=TRUE)
```

#### Material 60 (Kalkstein)

<https://www.eagle-network.eu/voc/material/lod/60.html>

```{r}
EDH_eagle %>% 
  filter(support_material == 60) %>% 
  count(support_material_text, sort=TRUE)
```

#### Material 75 (Sandstein)

<https://www.eagle-network.eu/voc/material/lod/75.html>

```{r}
EDH_eagle %>% 
  filter(support_material == 75) %>% 
  count(support_material_text, sort=TRUE)
```

#### Material 48 (Marmor)

<https://www.eagle-network.eu/voc/material/lod/48.html>

```{r}
EDH_eagle %>% 
  filter(support_material == 48) %>% 
  count(support_material_text, sort=TRUE)
```

#### Material 131 (Arcilla)

<https://www.eagle-network.eu/voc/material/lod/131.html>

```{r}
EDH_eagle %>% 
  filter(support_material == 131) %>% 
  count(support_material_text, sort=TRUE)
```

#### Material 109 (Aes)

<https://www.eagle-network.eu/voc/material/lod/109.html>

```{r}
EDH_eagle %>% 
  filter(support_material == 109) %>% 
  count(support_material_text, sort=TRUE)
```

#### Material 108 (Plumbum)

<https://www.eagle-network.eu/voc/material/lod/108.html>

```{r}
EDH_eagle %>% 
  filter(support_material == 108) %>% 
  count(support_material_text, sort=TRUE)
```

#### Material 123 (Lignum)

<https://www.eagle-network.eu/voc/material/lod/123.html>

```{r}
EDH_eagle %>% 
  filter(support_material == 123) %>% 
  count(support_material_text, sort=TRUE)
```

#### Material 115 (Argentum)

<https://www.eagle-network.eu/voc/material/lod/115.html>

```{r}
EDH_eagle %>% 
  filter(support_material == 115) %>% 
  count(support_material_text, sort=TRUE)
```

### Material missing Eagle LOD, text present

Example: `<material>Marmor, geädert / farbig</material>`

```{r}
EDH_eagle %>% 
  select(support_material, support_material_text) %>% 
  filter(support_material == "") %>% 
  count(support_material_text, sort=TRUE)
```

### All unique values of text input

```{r}
unique(EDH_eagle$support_material_text)
```

## Writing

Attributes categorising the execution of writing, used `r writing_total` times.

XML: Layout tag, type execution.

Example of record in XML:

```         
<layout>
  <rs type="execution" ref="http://www.eagle-network.eu/voc/writing/lod/21">unbestimmt</rs>
</layout>
```

### Display the first six values for illustration

```{r}
EDH_eagle %>% 
  select(layout_execution, layout_execution_text) %>%
  head()
```

### List of all related Eagle vocabularies and their count

```{r}
EDH_eagle %>% 
  select(layout_execution, layout_execution_text) %>% 
  count(layout_execution, sort=TRUE)
```

### Total number of unique vocabularies

```{r}
length(unique(EDH_eagle$layout_execution))
```

### Overview of the ten most common vocabularies

#### Layout execution 21 (Ignoratur)

<https://www.eagle-network.eu/voc/writing/lod/21.html>

```{r}
EDH_eagle %>% 
  filter(layout_execution == 21) %>% 
  count(layout_execution_text, sort=TRUE)
```

#### Layout execution 88 (Geritzt)

<https://www.eagle-network.eu/voc/writing/lod/88.html>

```{r}
EDH_eagle %>% 
  filter(layout_execution == 88) %>% 
  count(layout_execution_text, sort=TRUE)
```

#### Layout execution 77 (gestempelt)

<https://www.eagle-network.eu/voc/writing/lod/77.html>

```{r}
EDH_eagle %>% 
  filter(layout_execution == 77) %>% 
  count(layout_execution_text, sort=TRUE)
```

#### Layout execution 96 (Gemalt / Dipinto)

<https://www.eagle-network.eu/voc/writing/lod/96.html>

```{r}
EDH_eagle %>% 
  filter(layout_execution == 96) %>% 
  count(layout_execution_text, sort=TRUE)
```

#### Layout execution 145 (gepunzt)

<https://www.eagle-network.eu/voc/writing/lod/145.html>

```{r}
EDH_eagle %>% 
  filter(layout_execution == 145) %>% 
  count(layout_execution_text, sort=TRUE)
```

#### Layout execution 23 (eingraviert)

<https://www.eagle-network.eu/voc/writing/lod/23.html>

```{r}
EDH_eagle %>% 
  filter(layout_execution == 23) %>% 
  count(layout_execution_text, sort=TRUE)
```

#### Layout execution 152 (mozaik)

<https://www.eagle-network.eu/voc/writing/lod/152.html>

```{r}
EDH_eagle %>% 
  filter(layout_execution == 152) %>% 
  count(layout_execution_text, sort=TRUE)
```

### Layout execution empty tag, but text present

```{r}
EDH_eagle %>% 
  filter(layout_execution == "") %>% 
  count(layout_execution_text, sort=TRUE)
```

### Layout execution NA (tag completely missing in XML)

```{r}
EDH_eagle %>% 
  select(layout_execution, layout_execution_text) %>% 
  filter(is.na(layout_execution)) %>% 
  count(layout_execution_text, sort=TRUE)
```

### All unique values of text input

```{r}
unique(EDH_eagle$layout_execution_text)
```

## Decoration

Attributes categorising the type of decoration. In EDH very limited use - not the full potential of LOD, used `r decor_total` times.

XML: Support, Rs tag, type decoration.

Example of record in XML:

```         
<rs type="decoration" ref="http://www.eagle-network.eu/voc/decor/lod/1000">nein</rs>
```

<https://www.eagle-network.eu/voc/decor/lod/1000.html> = nein

<https://www.eagle-network.eu/voc/decor/lod/2000.html>, 2000 = ja

NA = missing information

### Total number of unique vocabularies

```{r}
length(unique(EDH_eagle$support_decoration))
```

### List of all related Eagle vocabularies and their count

```{r}
EDH_eagle %>% 
  count(support_decoration, sort=TRUE)
```
