---
title: "Use of the existing Eagle project vocabularies in the ICyrenaica dataset"
author:
- Petra Hermankova^[Johannes Gutenberg University in Mainz, petra.hermankova@uni-mainz.de, https://orcid.org/0000-0002-6349-0540]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: united
    toc: yes
    toc_float: true
    number_sections: true
    toc_depth: 2
    df_print: paged
---

**The aim of this script is to analyse the usage of EAGLE vocabularies in the I.Sicily as part of the FAIR Epigraphy project and the Epigraphy.info working group tasked with cleaning up the EAGLE vocabularies.**

## Environment setup

```{r setup, echo=TRUE, message=FALSE}
library(tidyverse)
library(jsonlite)
library(zen4R)
library(xml2)
library(XML)
```

# Data loading and preparation

##  Load the latest ICyr dataset directly from their website

```{r}

# Does not work , solve 

# download.file("https://ircyr2020.inslib.kcl.ac.uk/en/inscriptions/zip/", "ICyr.zip")

```

## Extract the Zenodo repository
```{r}
unzip(filename, exdir = "./data/ICyr")
```

## Read and parse the XML files and extract the vocabularies data into a CSV, using python script

We are looking specifically for vocabularies `terms` that contain information about the type of an inscription
`<textClass>`
  `<keywords scheme="http://www.eagle-network.eu/voc/typeins.html">`
    `<term key="funerary" ref="http://www.eagle-network.eu/voc/typeins/lod/92.html">funerary</term>`
  `</keywords>`
`</textClass>`

```{r}
# Enabling reticulate library to run the python scripts within R
library(reticulate)
```

```{python}
# Read and parse the XML files and extract the vocabularies data into a CSV, using python script

#!/usr/bin/env python3
# Epidoc to csv converter
# written by Brian Ballsun-Stanton
# under a MIT License

import glob
import csv
import epidoc
import shutil
import os
import tqdm
import json
import numpy as np
import pandas as pd


PROJECT = "ICyr"
SOURCE_DIR = "./data/ICyr"
TARGET_DIR = "xml_to_csv"

# clean target dir by deleting and recreating
# shutil.rmtree(TARGET_DIR, ignore_errors=True)
# os.mkdir(TARGET_DIR)

docs = []

# get all files in source dir
for i, file in enumerate(tqdm.tqdm(glob.glob(f"{SOURCE_DIR}/*.xml"))):
    with open(file) as f:
        doc = epidoc.load(f)
    docs.append(doc)
    # if i > 10:
    #     break
    # break

output_docs = []


# Get Title, All instances of idno and terms
# Terms hide under textClass

max_terms = 0

for doc in tqdm.tqdm(docs):
    line = {}
    line["title"] = doc.title
    line["idno"] = doc.idno
    for i, term in enumerate(doc.terms):
        # prepend _{i} to each key inside term
        for key in term.copy().keys():
            term[f"term_{key}_{i}"] = term.pop(key) 
        line[f"term_{i}"] = term
        if max_terms < i:
            max_terms = i

    output_docs.append(line)



# Write to JSON
with open(f"{TARGET_DIR}/{PROJECT}_type_of_inscriptions.json", "w") as f:
    json.dump(output_docs, f, indent=4)



# Make output_docs a dataframe
df = pd.DataFrame(output_docs)
# flatten the idno dictionary into the dataframe
df = pd.concat([df.drop(["idno"], axis=1), df["idno"].apply(pd.Series)], axis=1)
for i in range(max_terms+1):
    print(i)
    df = pd.concat([df.drop([f"term_{i}"], axis=1), df[f"term_{i}"].apply(pd.Series)], axis=1)

# Write to CSV
df.to_csv(f"{TARGET_DIR}/{PROJECT}_type_of_inscriptions.csv", index=False)


```
As a result, ICyr does not use the tyep of inscription vocabulary.



